\textit{Extended data for}: Towards human Super EEG?

### 2018-10-11 paper/boneyard.tex

% old discussion section

>>>>

% old discussion section
Human \textit{SuperEEG}\footnote{The term ``SuperEEG'' was coined by
    Robert J. Sawyer in his popular science fiction novel \textit{The
      Terminal Experiment}~\cite{Sawy95}.  SuperEEG is a fictional
    technology that measures ongoing
  neural activity throughout the entire living human brain with perfect
  precision and at arbitrarily high spatiotemporal resolution.}
